Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-16 surfaces-write-up/surface-write-up.tex
some edits on proof of relations

\begin{lem}\label{P-m-relations-psi}
$\ker(\psi)$ is generated in degrees up to
\[
	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
\]
\end{lem}
\begin{proof}
We first claim there exist $\beta_1, \ldots, \beta_n \in k[\Sigma]$ such that $\ker \psi$ is generated by
\begin{equation}\label{eqn:relations-psi-P-n}
	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
\end{equation}

@@

To find such a $\beta_i$, we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_{m+1}$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{r_i}$ to a canonical form as given by Proposition \ref{prop:cone-generation}.

We now fix $z_i$ and bound the degree of generation of this set of relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$.  We first associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1, \ldots, c_n)$ where $d$ is its degree.  Let $\Sigma_i \subseteq \mathbb{Z}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.  
Then we see $\Sigma_i$ is contained in the $\mathbb{R}_{\ge 0}$-span of $e_1, \ldots, e_n$ (as defined in Equation \ref{defn:e_i-P-n}) translated by by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.

>>>>

\begin{lem}\label{P-m-relations-psi}
$\ker(\psi)$ is generated in degrees up to
\begin{align}
\label{eqn:pm-relation-degree}
	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
\end{align}

\end{lem}
\begin{proof}
We first claim there exist $\beta_1, \ldots, \beta_n \in k[\Sigma]$ such that $\ker \psi$ is generated by
\begin{equation}\label{eqn:pm-relations-psi}
	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
\end{equation}

@@

We define the $\beta_i$ above so that $\beta_i$ is the expansion of $f_i$ when viewed as a polynomial in $k[f_1,\ldots, f_{m+1}]$. Furthermore, the relations given in Equation ~\eqref{eqn:pm-relations-psi}
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{r_i}$ to a canonical form as given by Proposition \ref{prop:cone-generation}.

For the remainder of the proof, fix $i \in \{1,\ldots, n\}$. 
To complete the proof, it suffices to bound the degree of generation of the relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$, by Equation ~\eqref{eqn:pm-relation-degree}.  We first associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1, \ldots, c_n)$ where $d$ is its degree.  Let $\Sigma_i \subseteq \mathbb{Z}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.  
Then we see $\Sigma_i$ is contained in the $\mathbb{R}_{\ge 0}$-span of $e_1, \ldots, e_n$ (as defined in Equation \ref{defn:e_i-P-n}) translated by by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
